Paper Figs

### 2023-11-17 graphs_newt_snakes/Paper_figs.Rmd
more figure edit

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(gridtext)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(stringr)
library(patchwork)
library(RColorBrewer)
library(scales)
```

@@

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

@@

cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
cost_grade_cor$exp="Cost Gradent Map"

@@

cost_grade_no_interact_cor<- read.csv("~/Desktop/no_interaction_cost_grade/all_cor.txt" , header = TRUE)
cost_grade_no_interact_cor$group_rep <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd, "_", cost_grade_no_interact_cor$rep)
cost_grade_no_interact_cor$group <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd)
cost_grade_no_interact_cor$sim=LETTERS[factor(cost_grade_no_interact_cor$group)]
cost_grade_no_interact_cor$exp="Cost Gradent Map No Interaction"

snake_change_cor<- read.csv("~/Desktop/snake_change/all_cor.txt" , header = TRUE)
snake_change_cor$group_rep <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd, "_", snake_change_cor$rep)
snake_change_cor$group <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd)
snake_change_cor$sim=LETTERS[factor(snake_change_cor$group)]
snake_change_cor$exp="Snake Gradent Map"

@@

boxplot_cors_by_gen_col_rep <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)

@@

#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map"))

@@

boxplot_cors_by_gen_col_rep_other3 <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)

@@

#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
file$exp = factor(file$exp, levels=c("Cost Gradent Map No Interaction", "Snake Gradent Map", "Newt Gradent Map"))

@@

boxplot_cors_by_gen_col_rep_6_file <- function(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
    file4$snake_newt <- paste0(file4$snake_mu_rate, "_", file4$snake_mu_effect_sd, "_", file4$newt_mu_rate, "_", file4$newt_mu_effect_sd)
   file5$snake_newt <- paste0(file5$snake_mu_rate, "_", file5$snake_mu_effect_sd, "_", file5$newt_mu_rate, "_", file5$newt_mu_effect_sd)
   file6$snake_newt <- paste0(file6$snake_mu_rate, "_", file6$snake_mu_effect_sd, "_", file6$newt_mu_rate, "_", file6$newt_mu_effect_sd)
file <- rbind(file1, file2, file3, file4, file5, file6)

@@

file$exp = factor(file$exp, levels=c("Flat Map", "Cost Gradent Map No Interaction", "Cost Gradent Map", "Snake Gradent Map", "Interaction Gradent Map", "Newt Gradent Map"))

@@

file1 = GA1_cor
file2 = cost_grade_cor
file3 = interrate_grade
file4 = cost_grade_no_interact_cor
file5 = snake_change_cor
file6 = newt_change_cor
title = "Spatial Phenotype Correlation"
subt = " "
exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
x_label = "Newt/Snake Genetic Architecture"
y_label = "Spatial Correlation"
min_gen = 40000
max_gen = 50000

@@

boxplot_dif_in_phenotype <- function(file, title, subt, x_label, y_label,gen_l, gen_h,lowest){

@@

@@

data$order = paste0("(",data$mv_dif,")", data$snake_newt)

@@

plot <-   
ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(value),fill=name), alpha=0.3)+
  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(Snake_mean_Pheno),fill=name),  alpha=0.3)+
  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(dif),fill=name), alpha=0.3)+ # group=paste0(mv_dif,snake_newt)
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_dif_in_phopulationsize <- function(file, title, subt, x_label, y_label, gen_l, gen_h, lowest){

@@

plot <-    ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value),  fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_dif_in_phenotype_less_log <- function(file, title, subt, x_label, y_label,gen_l, gen_h){

@@

data$order = paste0("(",data$mv_dif,")", data$snake_newt)
data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))

plot <-   
  ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))
  return(plot)
}

boxplot_dif_in_phopulationsize_less_log <- function(file, title, subt, x_label, y_label, gen_l, gen_h){

   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$dif = file$Snake_pop_size- file$Newt_pop_size
file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))

@@

data$order = paste0("(",data$mv_dif,")", data$snake_newt)
data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))

plot <-    ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))
  return(plot)
}

gen_l=45000
gen_h=50000
lowest="1e-08_0.005"
title="Phenotype Difference by Mutatinal Varance"
subt="Experiment GA1_lit"
x_label = "Sanke GA - Newt GA"
y_label = "Difference in Phenotype (Snake - Newt)"
boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size (Snake - Newt)"
boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment mu_a_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-08_0.005"
boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_b_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
lowest="1e-09_0.0158"
boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_c_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-10_0.05"
boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-11_0.158"
boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment v_a_lit" 
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_b_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_c_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)

>>>>

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(gridtext)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(stringr)
library(patchwork)
library(RColorBrewer)
library(scales)
library(cowplot)
```

@@

snewt <- 0.71 #correlation value from https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.0060060

@@

cost_grade_cor<- read.csv("~/Desktop/cost_grade/all_cor.txt" , header = TRUE)
cost_grade_cor$group_rep <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd, "_", cost_grade_cor$rep)
cost_grade_cor$group <- paste0(cost_grade_cor$snake_mu_rate, "_", cost_grade_cor$snake_mu_effect_sd,"_",cost_grade_cor$newt_mu_rate, "_", cost_grade_cor$newt_mu_effect_sd)
cost_grade_cor$sim=LETTERS[factor(cost_grade_cor$group)]
cost_grade_cor$exp="Heterogeneous Cost Map"

@@

cost_grade_no_interact_cor<- read.csv("~/Desktop/no_interaction_cost_grade/all_cor.txt" , header = TRUE)
cost_grade_no_interact_cor$group_rep <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd, "_", cost_grade_no_interact_cor$rep)
cost_grade_no_interact_cor$group <- paste0(cost_grade_no_interact_cor$snake_mu_rate, "_", cost_grade_no_interact_cor$snake_mu_effect_sd,"_",cost_grade_no_interact_cor$newt_mu_rate, "_", cost_grade_no_interact_cor$newt_mu_effect_sd)
cost_grade_no_interact_cor$sim=LETTERS[factor(cost_grade_no_interact_cor$group)]
cost_grade_no_interact_cor$exp="Heterogeneous Cost Map No Interaction"

snake_change_cor<- read.csv("~/Desktop/snake_change/all_cor.txt" , header = TRUE)
snake_change_cor$group_rep <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd, "_", snake_change_cor$rep)
snake_change_cor$group <- paste0(snake_change_cor$snake_mu_rate, "_", snake_change_cor$snake_mu_effect_sd,"_",snake_change_cor$newt_mu_rate, "_", snake_change_cor$newt_mu_effect_sd)
snake_change_cor$sim=LETTERS[factor(snake_change_cor$group)]
snake_change_cor$exp="Snake Heterogeneous Cost Map"

@@

boxplot_cors_by_gen_col_rep <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){

  real_snewt_cor = snewt
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)

@@

#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
file$exp = factor(file$exp, levels=c("Flat Map", "Heterogeneous Cost Map", "Interaction Gradent Map"))

@@

boxplot_cors_by_gen_col_rep_other3 <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = snewt
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)

@@

#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
file$exp = factor(file$exp, levels=c("Heterogeneous Cost Map No Interaction", "Snake Heterogeneous Cost Map", "Newt Heterogeneous Cost Map"))

@@

boxplot_cors_by_gen_col_rep_6_file <- function(file1, file2, file3, file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = snewt
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
    file4$snake_newt <- paste0(file4$snake_mu_rate, "_", file4$snake_mu_effect_sd, "_", file4$newt_mu_rate, "_", file4$newt_mu_effect_sd)
   file5$snake_newt <- paste0(file5$snake_mu_rate, "_", file5$snake_mu_effect_sd, "_", file5$newt_mu_rate, "_", file5$newt_mu_effect_sd)
   file6$snake_newt <- paste0(file6$snake_mu_rate, "_", file6$snake_mu_effect_sd, "_", file6$newt_mu_rate, "_", file6$newt_mu_effect_sd)
file <- rbind(file1, file2, file3, file4, file5, file6)

@@

file$exp = factor(file$exp, levels=c("Flat Map", "Heterogeneous Cost Map No Interaction", "Heterogeneous Cost Map", "Snake Heterogeneous Cost Map", "Interaction Gradent Map", "Newt Heterogeneous Cost Map"))

@@

file1 = GA1_cor
file2 = cost_grade_cor
file3 = interrate_grade
file4 = cost_grade_no_interact_cor
file5 = snake_change_cor
file6 = newt_change_cor
title = "Spatial Phenotype Correlation"
subt = " "
exp_labeles=c("Flat Map", "Heterogeneous Cost Map", "Interaction Gradent Map")
x_label = "Newt/Snake Genetic Architecture"
y_label = "Spatial Correlation"
min_gen = 40000
max_gen = 50000

@@

boxplot_dif_in_phenotype <- function(file, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter){

@@

file$sim_snake_name = NA
  file$sim_newt_name = NA
  #file$sim == "A" | "B" | "C" | "D"
  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)

@@

data$order = paste0("(",round(data$mv_dif),")", data$sim_name)

@@

plot <-   
ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(value),fill=name), alpha=0.3)+
  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(Snake_mean_Pheno),fill=name),  alpha=0.3)+
  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(dif),fill=name), alpha=0.3)+ # group=paste0(mv_dif,snake_newt)
  scale_fill_manual(values=c(Newt_mean_Pheno="red",Snake_mean_Pheno="blue",dif="purple"),breaks=c('Newt_mean_Pheno','Snake_mean_Pheno','dif'), labels=c( "Newt Phenotype", "Snake Phenotype", "Phenotype Difference (S-N)"), name="Mean")+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_dif_in_phopulationsize <- function(file, title, subt, x_label, y_label, gen_l, gen_h, lowest, letter){

@@

plot <-    ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value),  fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  scale_fill_manual(values=c(Newt_pop_size="red",Snake_pop_size="blue",dif="green"),breaks=c('Newt_pop_size','Snake_pop_size','dif'), labels=c( "Newt Population Size", "Snake Population Size", "Population Size Difference (S-N)"), name="Population Size")+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

boxplot_dif_in_phenotype_less_log <- function(file, title, subt, x_label, y_label,gen_l, gen_h, letter){

@@

data$order = paste0("(",data$mv_dif,")", data$sim_name)
data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))

plot <-   
  ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  scale_fill_manual(values=c(Newt_mean_Pheno="red",Snake_mean_Pheno="blue",dif="purple"),breaks=c('Newt_mean_Pheno','Snake_mean_Pheno','dif'), labels=c( "Newt Phenotype", "Snake Phenotype", "Phenotype Difference (S-N)"), name="Mean")+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))
  return(plot)
}

boxplot_dif_in_phopulationsize_less_log <- function(file, title, subt, x_label, y_label, gen_l, gen_h,  letter){

   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$dif = file$Snake_pop_size- file$Newt_pop_size
file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))
file$sim_snake_name = NA
  file$sim_newt_name = NA
  #file$sim == "A" | "B" | "C" | "D"
  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)

@@

data$order = paste0("(",data$mv_dif,")", data$sim_name)
data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))

plot <-    ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  scale_fill_manual(values=c(Newt_pop_size="red",Snake_pop_size="blue",dif="green"),breaks=c('Newt_pop_size','Snake_pop_size','dif'), labels=c( "Newt Population Size", "Snake Population Size", "Population Size Difference (S-N)"), name="Population Size")+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))
  return(plot)
}

gen_l=45000
gen_h=50000
lowest="1e-08_0.005"
title="Phenotype Difference by Mutational Variance"
subt="Experiment GA1_lit"
letter="a"
x_label = "Snake GA - Newt GA"
y_label = "Phenotype"
ga1pp = boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
ga1ps = boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)

pg1 = plot_grid(ga1pp, ga1ps, labels = c('A', 'B'), label_size = 12, nrow =2)
ggsave("PD_PSD.png", plot=pg1, height=7, width=7, units=c("in"), dpi=600)

title="Phenotype Difference by Mutational Variance" 
subt="Experiment mu_a_lit"
letter="b"
x_label = "Simulations"
y_label = "Phenotype"
lowest="1e-08_0.005"
mu_a = boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
mu_a
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)

title="Phenotype Difference by Mutational Variance"
subt="Experiment mu_b_lit"
letter="c"
x_label = "Simulations" 
y_label = "Phenotype"
lowest="1e-09_0.0158"
mu_b = boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
mu_b
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)

title="Phenotype Difference by Mutational Variance"
subt="Experiment mu_c_lit" 
letter="d"
x_label = "Simulations"
y_label = "Phenotype"
lowest="1e-10_0.05"
mu_c = boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
mu_c
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)

title="Phenotype Difference by Mutational Variance"
subt="Experiment mu_d_lit" 
letter="e"
x_label = "Simulations"
y_label = "Phenotype"
lowest="1e-11_0.158"
mu_d = boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest, letter)

pg1 = plot_grid(mu_a, mu_b, mu_c, mu_d, labels = c('A', 'B', "C", "D"), label_size = 12)
ggsave("mus_app.png", plot=pg1, height=7, width=10, units=c("in"), dpi=600)

title="Phenotype Difference by Mutational Variance" 
subt="Experiment v_a_lit" 
letter="f"
x_label = "Simulations" 
y_label = "Phenotype"
v_a = boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
v_a
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)

title="Phenotype Difference by Mutational Variance"
subt="Experiment v_b_lit"
letter="g"
x_label = "Simulations"
y_label = "Phenotype"
v_b = boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
v_b
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)

title="Phenotype Difference by Mutational Variance"
subt="Experiment v_c_lit"
letter="h"
x_label = "Simulations" 
y_label = "Phenotype"
v_c = boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
v_c
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)

title="Phenotype Difference by Mutational Variance"
subt="Experiment v_d_lit" 
letter="i"
x_label = "Simulations"
y_label = "Phenotype"
v_d = boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)
title="Population size Difference by Mutational Variance"
y_label = "Population Size"
boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h, letter)

pg2 = plot_grid(v_a, v_b, v_c, v_d, labels = c('A', 'B', "C", "D"), label_size = 12)
ggsave("vms_app.png", plot=pg2, height=7, width=10, units=c("in"), dpi=600)
